---
title: "Model Training and Querying Template"
author: "Jonathan Fitzgerald & Sarah Connell"
date: "7/25/2025"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using this File

This file is set up to enable testing of models to be included in the toolkit. 

## Loading packages

```{r}

library(tidyverse)
library(tidytext)
library(magrittr)
library(devtools)
library(tsne)
library(wordVectors)
library(ggplot2)
library(lsa)

```

## Reading in existing model files
You don't need to run this if you want to work with a file you just trained; but if you would like to switch models or read in an existing one after starting a new session, this is the code you would use.
 
```{r}

w2vModel <- read.vectors("data/name_of_your_file.bin")

```

## Clustering

```{r}

centers <- 150
clustering <- kmeans(w2vModel, centers=centers, iter.max=40)

sapply(sample(1:centers, 100), function(n) {
  names(clustering$cluster[clustering$cluster==n][1:15])
})

```

## Closest to

```{r}

#To have the results appear in the console below
w2vModel %>% closest_to("girl", 30) 

```


## Exporting clusters

```{r}

#Change "name_of_your_cluster" to a descriptive name that you want to give to your export file.
centers <- 150

clustering <- kmeans(w2vModel,centers=centers,iter.max = 40)

w2vExport <-sapply(sample(1:centers,150),function(n) {
  names(clustering$cluster[clustering$cluster==n][1:15])
})

write.csv(file="output/name_of_your_cluster.csv", x=w2vExport)

```

## Evaluating the Model


```{r}

files_list = list.files(pattern = "*.bin$", recursive = TRUE)

rownames <- c()

data_frame <- data.frame()
data = list(c("acquainted", "unacquainted"),
c("acquainted", "conversant"),
c("acquainted", "known"),
c("advantage", "disadvantage"),
c("affairs", "concerns"),
c("affairs", "finances"),
c("affairs", "matters"),
c("affairs", "business"),
c("affairs", "interests"),
c("affection", "fondness"),
c("affection", "tenderness"),
c("affection", "love"),
c("affection", "sympathy"),
c("affection", "kindness"),
c("affection", "friendship"),
c("affection", "esteem"),
c("afraid", "scared"),
c("afraid", "frightened"),
c("agreeable", "disagreeable"),
c("agreeable", "displeasing"),
c("agreeable", "pleasant"),
c("agreeable", "delightful"),
c("agreeable", "pleasing"),
c("air", "atmosphere"),
c("air", "sky"),
c("air", "aether"),
c("air", "æther"),
c("air", "vapor"),
c("air", "vapour"),
c("air", "breeze"),
c("air", "element"),
c("allow", "permit"),
c("allow", "authorize"),
c("allow", "refuse"),
c("allowed", "permitted"),
c("allowed", "admitted"),
c("allowed", "required"),
c("allowed", "authorized"),
c("allowed", "authorised"),
c("alone", "solitary"),
c("always", "constantly"),
c("always", "invariably"),
c("always", "often"),
c("always", "seldom"),
c("always", "never"),
c("always", "sometimes"),
c("always", "generally"),
c("always", "frequently"),
c("america", "north"),
c("america", "south"),
c("america", "africa"),
c("america", "europe"),
c("america", "asia"),
c("america", "states"),
c("america", "colonies"),
c("america", "continent"),
c("america", "england"),
c("america", "indies"),
c("america", "ireland"),
c("america", "britain"),
c("america", "canada"),
c("america", "mexico"),
c("ancient", "modern"),
c("ancient", "old"),
c("ancient", "traditional"),
c("ancient", "antique"),
c("animal", "vegetable"),
c("animals", "fishes"),
c("animals", "insects"),
c("animals", "mammals"),
c("animals", "reptiles"),
c("animals", "birds"),
c("appearance", "aspect"),
c("appearance", "figure"),
c("appointed", "nominated"),
c("appointed", "deputed"),
c("appointed", "elected"),
c("appointed", "ordained"),
c("appointed", "installed"),
c("appointed", "chosen"),
c("arm", "hand"),
c("arm", "wrist"),
c("arm", "shoulder"),
c("arms", "hands"),
c("arms", "paws"),
c("arms", "legs"),
c("army", "troops"),
c("army", "regiments"),
c("army", "cavalry"),
c("army", "brigade"),
c("army", "detachment"),
c("army", "regiment"),
c("army", "forces"),
c("army", "squadron"),
c("arrived", "returned"),
c("arrived", "reached"),
c("arts", "sciences"),
c("attempt", "endeavor"),
c("attempt", "endeavour"),
c("attempt", "undertake"),
c("attempt", "effort"),
c("authority", "jurisdiction"),
c("authority", "supremacy"),
c("authority", "primacy"),
c("authority", "sovereignty"),
c("authority", "prerogative"),
c("authority", "validity"),
c("authors", "writers"),
c("authors", "composers"),
c("authors", "translators"),
c("authors", "editors"),
c("authors", "compilers"),
c("authors", "commentators"),
c("authors", "critics"),
c("authors", "novelists"),
c("authors", "poets"),
c("authors", "biographers"),
c("authors", "dramatists"),
c("authors", "essayists"),
c("authors", "antiquaries"),
c("authors", "satirists"),
c("authors", "historians"),
c("authors", "journalists"),
c("back", "front"),
c("back", "forward"),
c("battle", "war"),
c("battle", "fight"),
c("bear", "endure"),
c("bear", "sustain"),
c("bear", "suffer"),
c("bear", "receive"),
c("bear", "wield"),
c("bear", "carry"),
c("bear", "hold"),
c("beauty", "loveliness"),
c("beauty", "charms"),
c("beauty", "graces"),
c("beauty", "elegance"),
c("beauty", "grandeur"),
c("beauty", "excellence"),
c("beauty", "splendour"),
c("beauty", "splendor"),
c("beauty", "brilliance"),
c("beauty", "charm"),
c("beauty", "ugliness"),
c("bed", "couch"),
c("bed", "sofa"),
c("bed", "pillow"),
c("bed", "pillows"),
c("bed", "quilt"),
c("bed", "blanket"),
c("bed", "bedroom"),
c("bed", "chamber"),
c("bed", "bedchamber"),
c("begin", "end"),
c("begin", "commence"),
c("begin", "proceed"),
c("beginning", "end"),
c("behold", "see"),
c("behold", "view"),
c("behold", "look"),
c("best", "worst"),
c("best", "finest"),
c("best", "greatest"),
c("better", "worse"),
c("birds", "insects"),
c("birds", "lizards"),
c("birds", "fishes"),
c("birds", "animals"),
c("birds", "reptiles"),
c("birds", "blackbirds"),
c("birds", "ravens"),
c("birds", "buzzards"),
c("birds", "goldfinches"),
c("birds", "owls"),
c("birds", "sparrows"),
c("birds", "crows"),
c("birds", "falcons"),
c("birds", "fowls"),
c("blessed", "happy"),
c("blessed", "glorified"),
c("blood", "veins"),
c("blood", "heart"),
c("blood", "cheeks"),
c("blood", "flesh"),
c("blood", "vitals"),
c("body", "soul"),
c("body", "mind"),
c("body", "spirit"),
c("body", "skin"),
c("body", "limbs"),
c("body", "bones"),
c("body", "frame"),
c("body", "flesh"),
c("body", "meat"),
c("book", "paper"),
c("book", "paragraph"),
c("book", "chapters"),
c("book", "printer"),
c("book", "reader"),
c("book", "author"),
c("book", "writer"),
c("book", "publisher"),
c("book", "compiler"),
c("book", "editor"),
c("book", "bookseller"),
c("book", "tome"),
c("book", "volume"),
c("book", "folio"),
c("book", "pamphlet"),
c("book", "manuscript"),
c("book", "notebook"),
c("book", "treatise"),
c("book", "edition"),
c("books", "manuscripts"),
c("books", "novels"),
c("books", "bibles"),
c("books", "poems"),
c("books", "letters"),
c("books", "biographies"),
c("books", "sermons"),
c("books", "libraries"),
c("books", "library"),
c("born", "bred"),
c("born", "died"),
c("bosom", "breast"),
c("bosom", "heart"),
c("bosom", "chest"),
c("bosom", "soul"),
c("bound", "pinioned"),
c("bound", "tied"),
c("bound", "chained"),
c("bound", "compelled"),
c("bound", "fettered"),
c("bound", "tied"),
c("bound", "tyed"),
c("bound", "manacled"),
c("boy", "girl"),
c("boy", "lad"),
c("boy", "child"),
c("break", "rip"),
c("break", "shake"),
c("break", "throw"),
c("break", "destroy"),
c("breast", "bosom"),
c("breast", "heart"),
c("breast", "chest"),
c("bright", "dark"),
c("bright", "dim"),
c("bright", "shining"),
c("bright", "radiant"),
c("bright", "resplendent"),
c("bright", "lustrous"),
c("bright", "dazling"),
c("bright", "dazzling"),
c("bright", "beaming"),
c("bright", "sparkling"),
c("british", "english"),
c("british", "american"),
c("british", "scottish"),
c("british", "swedish"),
c("british", "scandinavian"),
c("british", "danish"),
c("british", "scottish"),
c("british", "french"),
c("british", "canadian"),
c("british", "austrian"),
c("british", "polish"),
c("british", "spanish"),
c("british", "irish"),
c("brother", "father"),
c("brother", "grandfather"),
c("brother", "uncle"),
c("brother", "son"),
c("brother", "nephew"),
c("brother", "sister"),
c("built", "erected"),
c("built", "constructed"),
c("care", "pains"),
c("care", "heed"),
c("care", "caution"),
c("care", "trouble"),
c("care", "solicitude"),
c("care", "concern"),
c("castle", "abbey"),
c("castle", "priory"),
c("castle", "cathedral"),
c("castle", "tower"),
c("castle", "citadel"),
c("castle", "palace"),
c("castle", "fortress"),
c("certain", "real"),
c("certain", "incontestable"),
c("certain", "sure"),
c("certain", "particular"),
c("certain", "questionable"),
c("certain", "uncertain"),
c("certainly", "undoubtedly"),
c("certainly", "surely"),
c("certainly", "doubtless"),
c("certainly", "really"),
c("certainly", "indisputably"),
c("certainly", "incontestably"),
c("certainly", "assuredly"),
c("certainly", "probably"),
c("certainly", "likely"),
c("change", "alteration"),
c("change", "mutation"),
c("change", "vicissitude"),
c("change", "fluctuation"),
c("change", "variation"),
c("change", "alter"),
c("change", "vary"),
c("change", "modify"),
c("change", "adjust"),
c("character", "trait"),
c("charms", "beauties"),
c("charms", "graces"),
c("charms", "fascinations"),
c("charms", "attractions"),
c("charms", "allurements"),
c("chief", "principal"),
c("chief", "sole"),
c("chief", "general"),
c("child", "parent"),
c("child", "daughter"),
c("child", "son"),
c("children", "parents"),
c("children", "grandparents"),
c("children", "husbands"),
c("children", "wives"),
c("children", "mothers"),
c("children", "fathers"),
c("children", "families"),
c("children", "playmates"),
c("children", "babies"),
c("children", "babes"),
c("children", "girls"),
c("children", "boys"),
c("children", "daughters"),
c("children", "sons"),
c("children", "grandchildren"),
c("children", "grandsons"),
c("children", "granddaughters"),
c("children", "sisters"),
c("children", "brothers"),
c("children", "nephews"),
c("children", "nieces"),
c("church", "congregation"),
c("church", "priest"),
c("church", "minister"),
c("church", "vicar"),
c("church", "pastor"),
c("church", "rector"),
c("church", "parson"),
c("church", "deacon"),
c("church", "deacons"),
c("church", "parsons"),
c("church", "rectors"),
c("church", "pastors"),
c("church", "vicars"),
c("church", "ministers"),
c("church", "congregations"),
c("church", "priests"),
c("church", "steeple"),
c("church", "vestry"),
c("church", "nave"),
c("church", "chapel"),
c("church", "cathedral"),
c("church", "baptist"),
c("church", "episcopal"),
c("church", "presbyterian"),
c("church", "unitarian"),
c("church", "methodist"),
c("church", "catholic"),
c("church", "congregationalist"),
c("church", "calvinist"),
c("church", "lutheran"),
c("city", "metropolis"),
c("city", "town"),
c("city", "suburbs"),
c("city", "seaport"),
c("city", "village"),
c("city", "neighborhood"),
c("city", "neighbourhood"),
c("city", "suburb"),
c("city", "suburbs"),
c("civil", "government"),
c("civil", "municipal"),
c("civil", "political"),
c("cold", "hot"),
c("cold", "warm"),
c("cold", "scorched"),
c("cold", "heat"),
c("cold", "chilly"),
c("cold", "damp"),
c("cold", "wet"),
c("cold", "frosty"),
c("cold", "foggy"),
c("cold", "frozen"),
c("cold", "freezing"),
c("cold", "icy"),
c("cold", "cool"),
c("cold", "chill"),
c("cold", "chiliness"),
c("cold", "heat"),
c("cold", "ice"),
c("cold", "sleet"),
c("cold", "snow"),
c("cold", "chiliness"),
c("cold", "chill"),
c("color", "red"),
c("color", "yellow"),
c("color", "blue"),
c("color", "green"),
c("color", "black"),
c("color", "white"),
c("come", "go"),
c("common", "uncommon"),
c("common", "particular"),
c("common", "anomalous"),
c("common", "extraordinary"),
c("common", "singular"),
c("common", "ordinary"),
c("common", "general"),
c("common", "conventional"),
c("company", "party"),
c("concerning", "respecting"),
c("concerning", "relating"),
c("concerning", "relative"),
c("conduct", "behavior"),
c("conduct", "behaviour"),
c("conduct", "manners"),
c("consider", "observe"),
c("consider", "reflect"),
c("consider", "examine"),
c("consider", "decipher"),
c("conversation", "discourse"),
c("conversation", "interviews"),
c("conversation", "interview"),
c("conversation", "discussion"),
c("conversation", "chitchat"),
c("council", "court"),
c("council", "senate"),
c("council", "assembly"),
c("council", "officials"),
c("council", "convocation"),
c("country", "land"),
c("country", "kingdom"),
c("country", "province"),
c("country", "island"),
c("country", "nation"),
c("country", "town"),
c("country", "city"),
c("country", "metropolis"),
c("country", "village"),
c("county", "shire"),
c("county", "township"),
c("county", "borough"),
c("courage", "valor"),
c("courage", "valour"),
c("courage", "bravery"),
c("courage", "fortitude"),
c("courage", "firmness"),
c("courage", "strength"),
c("courage", "resolution"),
c("courage", "indomitable"),
c("courage", "boldness"),
c("court", "council"),
c("court", "admiralty"),
c("court", "judicature"),
c("court", "assembly"),
c("court", "convocation"),
c("court", "officials"),
c("court", "chancellors"),
c("court", "senate"),
c("court", "chancery"),
c("court", "commissioners"),
c("creature", "woman"),
c("creature", "man"),
c("creature", "girl"),
c("creature", "boy"),
c("creature", "being"),
c("crown", "diadem"),
c("crown", "tiara"),
c("crown", "coronet"),
c("crown", "throne"),
c("crown", "regalia"),
c("crown", "mitre"),
c("crown", "scepter"),
c("crown", "sceptre"),
c("cruel", "inhuman"),
c("cruel", "inhumane"),
c("cruel", "merciless"),
c("cruel", "unkind"),
c("cruel", "brutal"),
c("dangerous", "safe"),
c("dangerous", "unsafe"),
c("dangerous", "hazardous"),
c("dangerous", "perilous"),
c("dangerous", "injurious"),
c("dark", "gloomy"),
c("dark", "cloudy"),
c("dark", "murky"),
c("dark", "shrouded"),
c("dark", "deep"),
c("dark", "dingy"),
c("dark", "gloom"),
c("dark", "shadowy"),
c("daughter", "sister"),
c("daughter", "niece"),
c("daughter", "aunt"),
c("daughter", "mother"),
c("daughter", "grandmother"),
c("daughter", "son"),
c("day", "night"),
c("day", "evening"),
c("day", "twilight"),
c("day", "midnight"),
c("day", "dusk"),
c("day", "morning"),
c("day", "afternoon"),
c("day", "dawn"),
c("day", "morn"),
c("day", "noon"),
c("day", "sunrise"),
c("day", "monday"),
c("day", "tuesday"),
c("day", "wednesday"),
c("day", "thursday"),
c("day", "friday"),
c("day", "saturday"),
c("day", "sunday"),
c("day", "sabbath"),
c("day", "sabbathday"),
c("day", "holydays"),
c("day", "month"),
c("day", "year"),
c("day", "hour"),
c("day", "week"),
c("days", "months"),
c("days", "weeks"),
c("days", "hours"),
c("days", "minutes"),
c("days", "seconds"),
c("days", "nights"),
c("days", "moments"),
c("days", "mornings"),
c("days", "evenings"),
c("days", "afternoons"),
c("dead", "alive"),
c("dead", "tomb"),
c("dead", "grave"),
c("dead", "sepulchre"),
c("dead", "sepulcher"),
c("dead", "buried"),
c("deep", "dark"),
c("deep", "fathomless"),
c("deep", "unfathomable"),
c("delight", "pleasure"),
c("delight", "joy"),
c("delight", "rapture"),
c("delight", "gladness"),
c("design", "intention"),
c("design", "scheme"),
c("design", "plan"),
c("design", "plot"),
c("design", "purpose"),
c("desire", "wish"),
c("desire", "passion"),
c("desire", "ardency"),
c("desire", "hope"),
c("desire", "longing"),
c("desired", "wished"),
c("desired", "requested"),
c("desired", "entreated"),
c("desired", "begged"),
c("desired", "wanted"),
c("desired", "hoped"),
c("desired", "longed"),
c("die", "perish"),
c("die", "expire"),
c("die", "bleed"),
c("die", "languish"),
c("die", "survive"),
c("die", "live"),
c("difference", "similarity"),
c("difference", "disparity"),
c("difference", "inequality"),
c("difference", "dissimilitude"),
c("difference", "distinction"),
c("difference", "dissimilarity"),
c("different", "same"),
c("different", "similar"),
c("different", "distinct"),
c("different", "dissimilar"),
c("different", "separate"),
c("different", "particular"),
c("different", "diverse"),
c("different", "peculiar"),
c("different", "disconnected"),
c("different", "various"),
c("different", "disagreeing"),
c("different", "several"),
c("difficulty", "inconvenience"),
c("difficulty", "impediment"),
c("difficulty", "trouble"),
c("discovered", "perceived"),
c("discovered", "observed"),
c("discovered", "noticed"),
c("discovered", "detected"),
c("discovered", "uncovered"),
c("discovered", "revealed"),
c("distant", "remote"),
c("distant", "far"),
c("doctor", "physician"),
c("doctor", "surgeon"),
c("doctor", "apothecary"),
c("doctor", "dentist"),
c("doctor", "chirurgeon"),
c("doctor", "midwife"),
c("door", "window"),
c("door", "gate"),
c("door", "latch"),
c("door", "casement"),
c("door", "lock"),
c("door", "doorway"),
c("door", "doorknob"),
c("door", "room"),
c("door", "house"),
c("door", "building"),
c("doubt", "believe"),
c("doubt", "expect"),
c("doubt", "know"),
c("doubt", "hope"),
c("doubt", "fear"),
c("doubt", "suspect"),
c("doubt", "suppose"),
c("drawn", "sketched"),
c("dress", "apparel"),
c("dress", "attire"),
c("dress", "costume"),
c("dress", "clothes"),
c("dress", "livery"),
c("dress", "habiliments"),
c("dress", "liveries"),
c("dress", "garb"),
c("dress", "uniform"),
c("dress", "embroidery"),
c("dress", "ribbons"),
c("dress", "gown"),
c("dress", "coat"),
c("dress", "petticoats"),
c("dress", "frock"),
c("dress", "suit"),
c("dress", "lace"),
c("dress", "jacket"),
c("dress", "shawl"),
c("duty", "obligation"),
c("duty", "fulfilment"),
c("duty", "obedience"),
c("earl", "baronet"),
c("earl", "viscount"),
c("earl", "duke"),
c("earl", "baron"),
c("earl", "count"),
c("earl", "marquess"),
c("earl", "countess"),
c("earl", "earldom"),
c("earth", "heaven"),
c("earth", "heavens"),
c("earth", "firmament"),
c("earth", "sky"),
c("earth", "skies"),
c("earth", "globe"),
c("ease", "complacence"),
c("ease", "contentment"),
c("ease", "tranquility"),
c("ease", "quietude"),
c("east", "west"),
c("east", "north"),
c("east", "south"),
c("east", "southwest"),
c("east", "southeast"),
c("east", "northwest"),
c("east", "northeast"),
c("easy", "difficult"),
c("easy", "tough"),
c("easy", "impossible"),
c("easy", "hard"),
c("easy", "practicable"),
c("easy", "expeditious"),
c("easy", "straightforward"),
c("easy", "tractable"),
c("education", "training"),
c("education", "learning"),
c("education", "instruction"),
c("education", "studies"),
c("education", "improvement"),
c("education", "school"),
c("education", "college"),
c("effects", "causes"),
c("effects", "consequences"),
c("effects", "results"),
c("employed", "engaged"),
c("employed", "enlisted"),
c("end", "beginning"),
c("end", "start"),
c("end", "middle"),
c("end", "last"),
c("end", "finish"),
c("end", "completion"),
c("end", "close"),
c("enemies", "adversaries"),
c("enemies", "foes"),
c("enemies", "persecutors"),
c("enemies", "invaders"),
c("enemies", "rebels"),
c("enemy", "invader"),
c("enemy", "foe"),
c("enemy", "rebel"),
c("enemy", "adversary"),
c("enemy", "persecutor"),
c("enemy", "rival"),
c("engaged", "employed"),
c("engaged", "engrossed"),
c("engaged", "occupied"),
c("engaged", "enlisted"),
c("engaged", "interested"),
c("engaged", "concerned"),
c("english", "british"),
c("english", "irish"),
c("english", "scotch"),
c("english", "welsh"),
c("english", "scottish"),
c("enough", "sufficient"),
c("epistles", "prefaces"),
c("epistles", "dissertations"),
c("epistles", "dialogues"),
c("epistles", "texts"),
c("epistles", "dedications"),
c("epistles", "treatises"),
c("epistles", "writings"),
c("epistles", "sermons"),
c("escape", "evade"),
c("escape", "elude"),
c("escape", "avoid"),
c("estate", "inheritance"),
c("estate", "patrimony"),
c("estate", "property"),
c("estate", "homestead"),
c("europe", "america"),
c("europe", "asia"),
c("europe", "africa"),
c("europe", "continent"),
c("europe", "germany"),
c("europe", "france"),
c("europe", "spain"),
c("europe", "england"),
c("europe", "italy"),
c("europe", "switzerland"),
c("europe", "holland"),
c("europe", "greece"),
c("europe", "poland"),
c("europe", "sweden"),
c("europe", "norway"),
c("europe", "denmark"),
c("europe", "netherlands"),
c("europe", "ireland"),
c("evening", "morning"),
c("evening", "afternoon"),
c("evening", "night"),
c("evening", "forenoon"),
c("evening", "noon"),
c("evening", "sunrise"),
c("evening", "daybreak"),
c("evening", "twilight"),
c("evening", "dusk"),
c("evil", "good"),
c("evil", "saintly"),
c("evil", "sainted"),
c("evil", "sinning"),
c("evil", "wickedness"),
c("evil", "sin"),
c("evil", "sinful"),
c("evil", "wicked"),
c("example", "instance"),
c("example", "pattern"),
c("example", "precedent"),
c("example", "sample"),
c("excellent", "admirable"),
c("excellent", "incomparable"),
c("excellent", "celebrated"),
c("excellent", "notable"),
c("excellent", "unparallelled"),
c("expect", "suppose"),
c("expect", "apprehend"),
c("expect", "imagine"),
c("expect", "hope"),
c("expected", "unexpected"),
c("expected", "surprising"),
c("expected", "unforeseen"),
c("expected", "hoped"),
c("expected", "imagined"),
c("expected", "wished"),
c("expected", "desired"),
c("expected", "anticipated"),
c("extraordinary", "uncommon"),
c("extraordinary", "surprising"),
c("extraordinary", "astonishing"),
c("extraordinary", "singular"),
c("extraordinary", "wonderful"),
c("extraordinary", "admirable"),
c("extraordinary", "amazing"),
c("extraordinary", "miraculous"),
c("extraordinary", "unparallelled"),
c("extraordinary", "particular"),
c("extraordinary", "unique"),
c("extraordinary", "anomalous"),
c("extremely", "exceedingly"),
c("extremely", "excessively"),
c("extremely", "uncommonly"),
c("extremely", "remarkably"),
c("extremely", "very"),
c("extremely", "highly"),
c("extremely", "prodigiously"),
c("extremely", "unusually"),
c("eye", "gaze"),
c("eye", "glance"),
c("eye", "sight"),
c("eye", "glances"),
c("eye", "see"),
c("eye", "eyebrow"),
c("eye", "lid"),
c("eye", "eyelid"),
c("eye", "lash"),
c("eye", "eyelash"),
c("eyes", "lids"),
c("eyes", "eyeballs"),
c("eyes", "sight"),
c("eyes", "seeing"),
c("eyes", "face"),
c("eyes", "nose"),
c("eyes", "ears"),
c("eyes", "lips"),
c("eyes", "mouth"),
c("face", "countenance"),
c("face", "visage"),
c("face", "features"),
c("face", "eye"),
c("face", "cheek"),
c("face", "forehead"),
c("face", "lips"),
c("face", "eyebrow"),
c("face", "eyebrows"),
c("face", "eyes"),
c("face", "nose"),
c("face", "mouth"),
c("fact", "reality"),
c("fact", "evidence"),
c("fact", "truth"),
c("fact", "hearsay"),
c("fact", "lie"),
c("fact", "fiction"),
c("fair", "lovely"),
c("fair", "beautiful"),
c("fair", "beauteous"),
c("fair", "charming"),
c("fair", "just"),
c("fair", "equitable"),
c("fair", "moral"),
c("fair", "ethical"),
c("faith", "belief"),
c("faith", "religion"),
c("faithful", "devoted"),
c("faithful", "pious"),
c("faithful", "dutiful"),
c("faithful", "loyal"),
c("faithful", "unfaithful"),
c("faithful", "disloyal"),
c("faithful", "wicked"),
c("false", "true"),
c("false", "dishonest"),
c("false", "insincere"),
c("false", "deceitful"),
c("false", "untrue"),
c("false", "deceptive"),
c("false", "deceiving"),
c("false", "counterfeit"),
c("false", "spurious"),
c("false", "calumnious"),
c("fame", "renown"),
c("fame", "glory"),
c("fame", "praise"),
c("fame", "reputation"),
c("fame", "merit"),
c("family", "mother"),
c("family", "parent"),
c("family", "brother"),
c("family", "sister"),
c("family", "uncle"),
c("family", "aunt"),
c("family", "grandfather"),
c("family", "grandmother"),
c("family", "husband"),
c("family", "wife"),
c("family", "grandparent"),
c("family", "nephew"),
c("family", "niece"),
c("family", "house"),
c("family", "neighborhood"),
c("family", "neighbourhood"),
c("family", "estate"),
c("family", "relations"),
c("family", "relatives"),
c("fancy", "imagination"),
c("fancy", "illusions"),
c("fancy", "illusion"),
c("fancy", "fiction"),
c("far", "remote"),
c("far", "distant"),
c("fatal", "disastrous"),
c("fatal", "dangerous"),
c("fatal", "deadly"),
c("fatal", "dire"),
c("fate", "destiny"),
c("fate", "doom"),
c("father", "mother"),
c("father", "parent"),
c("father", "brother"),
c("father", "sister"),
c("father", "uncle"),
c("father", "aunt"),
c("father", "grandfather"),
c("father", "grandmother"),
c("father", "husband"),
c("father", "wife"),
c("father", "son"),
c("father", "daughter"),
c("father", "grandchild"),
c("father", "nephew"),
c("father", "niece"),
c("fear", "dread"),
c("fear", "mistrust"),
c("fear", "distrust"),
c("fear", "despair"),
c("fear", "doubt"),
c("fear", "hope"),
c("fear", "trust"),
c("fear", "faith"),
c("feeling", "emotion"),
c("feeling", "sympathy"),
c("feeling", "sense"),
c("feeling", "sensibility"),
c("fell", "threw"),
c("fell", "dropped"),
c("fell", "sunk"),
c("fell", "sank"),
c("fell", "sprang"),
c("fell", "leaped"),
c("fell", "plunged"),
c("fell", "jumped"),
c("fell", "leapt"),
c("fell", "tumbled"),
c("fell", "flung"),
c("female", "male"),
c("female", "gender"),
c("female", "sex"),
c("field", "camp"),
c("field", "forest"),
c("field", "meadow"),
c("field", "barn"),
c("field", "plough"),
c("field", "ploughshare"),
c("field", "crop"),
c("filled", "crammed"),
c("filled", "overflowing"),
c("filled", "loaded"),
c("filled", "crowded"),
c("filled", "replete"),
c("find", "seek"),
c("find", "lose"),
c("find", "obtain"),
c("find", "get"),
c("find", "discover"),
c("find", "locate"),
c("find", "identify"),
c("find", "recognize"),
c("find", "gain"),
c("fire", "flames"),
c("fire", "embers"),
c("fire", "flame"),
c("fire", "smoke"),
c("fire", "cinders"),
c("fire", "smoak"),
c("fire", "ash"),
c("fire", "ashes"),
c("fire", "furnace"),
c("fire", "cauldron"),
c("fire", "stove"),
c("fire", "crucible"),
c("fire", "candle"),
c("fire", "flue"),
c("fire", "poker"),
c("fire", "tinder"),
c("fire", "faggot"),
c("fire", "bellows"),
c("fire", "charcoal"),
c("fire", "gunpowder"),
c("fire", "torch"),
c("fire", "kindling"),
c("fire", "heat"),
c("fixed", "immovable"),
c("fixed", "placed"),
c("fixed", "riveted"),
c("fixed", "unaltered"),
c("fixed", "stuck"),
c("followed", "accompanied"),
c("followed", "preceded"),
c("followed", "attended"),
c("followed", "led"),
c("followed", "pursued"),
c("following", "foregoing"),
c("following", "preceding"),
c("following", "leading"),
c("food", "sustenance"),
c("food", "nourishment"),
c("food", "victuals"),
c("food", "meal"),
c("food", "refreshment"),
c("food", "feast"),
c("food", "meat"),
c("food", "milk"),
c("food", "bread"),
c("food", "vegetables"),
c("force", "strength"),
c("force", "violence"),
c("force", "aggression"),
c("force", "power"),
c("force", "energy"),
c("force", "potency"),
c("force", "resistance"),
c("form", "shape"),
c("form", "frame"),
c("form", "figure"),
c("form", "outline"),
c("former", "latter"),
c("former", "preceding"),
c("former", "previous"),
c("former", "subsequent"),
c("fortune", "wealth"),
c("fortune", "affluence"),
c("fortune", "inheritance"),
c("fortune", "destiny"),
c("fortune", "luck"),
c("fortune", "fate"),
c("free", "enfranchised"),
c("free", "liberated"),
c("free", "emancipated"),
c("friend", "enemy"),
c("friend", "fellow"),
c("friend", "companion"),
c("friend", "compeer"),
c("friend", "playmate"),
c("friend", "colleague"),
c("friend", "acquaintance"),
c("friend", "neighbor"),
c("friend", "neighbour"),
c("friend", "confidant"),
c("friends", "enemies"),
c("friends", "companions"),
c("friends", "colleagues"),
c("friends", "acquaintances"),
c("friends", "neighbors"),
c("friends", "neighbours"),
c("friends", "relatives"),
c("friends", "brethren"),
c("friends", "confidants"),
c("friends", "fellows"),
c("friends", "cousins"),
c("friends", "brothers"),
c("friends", "sisters"),
c("friends", "relatives"),
c("friendship", "affection"),
c("friendship", "esteem"),
c("friendship", "amity"),
c("full", "empty"),
c("full", "brimming"),
c("full", "complete"),
c("full", "overflowing"),
c("garden", "greenhouse"),
c("garden", "orchard"),
c("garden", "park"),
c("garden", "meadow"),
c("garden", "field"),
c("generous", "disinterested"),
c("generous", "nobleminded"),
c("generous", "virtuous"),
c("generous", "noble"),
c("generous", "magnanimous"),
c("generous", "unselfish"),
c("generous", "liberal"),
c("generous", "benevolent"),
c("genius", "talents"),
c("genius", "excellence"),
c("genius", "talent"),
c("genius", "learning"),
c("genius", "originality"),
c("gentle", "mild"),
c("gentle", "soft"),
c("gentle", "tender"),
c("gentleman", "nobleman"),
c("gentleman", "noble"),
c("gentleman", "person"),
c("gentleman", "gentlewoman"),
c("gentleman", "baronet"),
c("gentleman", "viscount"),
c("gentleman", "duke"),
c("gentleman", "baron"),
c("gentleman", "count"),
c("gentleman", "marquess"),
c("gentleman", "earl"),
c("gentleman", "courtier"),
c("give", "bring"),
c("give", "send"),
c("give", "allow"),
c("give", "lend"),
c("give", "obtain"),
c("give", "take"),
c("give", "receive"),
c("give", "get"),
c("give", "borrow"),
c("given", "taken"),
c("given", "received"),
c("given", "borrowed"),
c("given", "obtained"),
c("given", "delivered"),
c("given", "assigned"),
c("given", "offered"),
c("given", "transmitted"),
c("given", "tendered"),
c("given", "vouchsafed"),
c("given", "sent"),
c("giving", "taking"),
c("giving", "sending"),
c("giving", "receiving"),
c("giving", "putting"),
c("glad", "sorry"),
c("glad", "sad"),
c("glad", "unhappy"),
c("glad", "miserable"),
c("glad", "happy"),
c("glad", "overjoyed"),
c("glad", "joyful"),
c("glad", "pleased"),
c("god", "lord"),
c("god", "almighty"),
c("god", "almightie"),
c("god", "creator"),
c("god", "savior"),
c("god", "saviour"),
c("god", "jehovah"),
c("god", "jesus"),
c("god", "christ"),
c("god", "heaven"),
c("gold", "silver"),
c("gold", "diamonds"),
c("gold", "rubies"),
c("gold", "pearls"),
c("gold", "jewels"),
c("gold", "gems"),
c("gold", "diamond"),
c("gold", "emeralds"),
c("gold", "pearl"),
c("gold", "emerald"),
c("gold", "ruby"),
c("gold", "sapphire"),
c("gold", "sapphires"),
c("gold", "coin"),
c("gold", "necklace"),
c("gold", "bracelet"),
c("gold", "earrings"),
c("good", "pleasing"),
c("good", "sanctified"),
c("good", "kind"),
c("good", "kindly"),
c("good", "kindlier"),
c("good", "saintly"),
c("good", "sainted"),
c("good", "bad"),
c("good", "evil"),
c("good", "wicked"),
c("government", "commonwealth"),
c("government", "monarchy"),
c("government", "republic"),
c("government", "theocracy"),
c("government", "parliamentary"),
c("government", "legislation"),
c("government", "establishment"),
c("government", "administration"),
c("government", "polity"),
c("government", "constitution"),
c("government", "nation"),
c("grave", "tomb"),
c("great", "good"),
c("great", "wonderful"),
c("great", "vast"),
c("great", "mighty"),
c("great", "prodigious"),
c("great", "infinite"),
c("great", "considerable"),
c("greater", "larger"),
c("greater", "higher"),
c("greater", "stronger"),
c("greater", "lesser"),
c("greater", "less"),
c("greater", "fewer"),
c("greater", "rarer"),
c("greater", "lighter"),
c("greater", "smaller"),
c("greater", "equal"),
c("greatly", "mightily"),
c("greatly", "considerably"),
c("greatly", "exceedingly"),
c("greatly", "highly"),
c("greatly", "much"),
c("greatly", "vastly"),
c("greatly", "prodigiously"),
c("greatly", "extremely"),
c("grief", "sorrow"),
c("grief", "anguish"),
c("grief", "woe"),
c("grief", "affliction"),
c("grief", "despair"),
c("grief", "distress"),
c("grief", "joy"),
c("ground", "turf"),
c("ground", "grass"),
c("ground", "mound"),
c("ground", "beach"),
c("ground", "pavement"),
c("ground", "sidewalk"),
c("ground", "sod"),
c("ground", "sand"),
c("ground", "hill"),
c("ground", "hillock"),
c("ground", "rock"),
c("ground", "sod"),
c("ground", "mountain"),
c("ground", "hillside"),
c("ground", "foot"),
c("ground", "feet"),
c("hair", "ringlets"),
c("hair", "curls"),
c("half", "whole"),
c("half", "quarter"),
c("half", "dozen"),
c("half", "million"),
c("half", "hundred"),
c("half", "thousand"),
c("half", "ten"),
c("half", "gallon"),
c("half", "quart"),
c("half", "pint"),
c("half", "score"),
c("half", "inch"),
c("half", "pound"),
c("hand", "arm"),
c("hand", "leg"),
c("hand", "elbow"),
c("hand", "shoulder"),
c("hand", "foot"),
c("hand", "fingers"),
c("hand", "wrist"),
c("hand", "palm"),
c("hand", "finger"),
c("hand", "glove"),
c("hand", "bracelet"),
c("hands", "fingers"),
c("hands", "wrists"),
c("hands", "palms"),
c("hands", "arms"),
c("hands", "legs"),
c("hands", "elbows"),
c("hands", "shoulders"),
c("hands", "feet"),
c("happy", "sad"),
c("happy", "unhappy"),
c("happy", "blessed"),
c("happy", "blest"),
c("happy", "fortunate"),
c("happy", "cheerful"),
c("happy", "prosperous"),
c("happy", "joyful"),
c("happy", "carefree"),
c("happy", "blissful"),
c("happy", "lighthearted"),
c("hard", "difficult"),
c("hard", "tough"),
c("hard", "easy"),
c("hardly", "scarcely"),
c("hardly", "never"),
c("hardly", "barely"),
c("hardly", "seldom"),
c("head", "shoulders"),
c("head", "elbow"),
c("head", "foot"),
c("head", "knee"),
c("head", "neck"),
c("head", "arms"),
c("head", "legs"),
c("head", "elbows"),
c("head", "face"),
c("head", "eyes"),
c("head", "lips"),
c("head", "chin"),
c("head", "brow"),
c("head", "nose"),
c("head", "ears"),
c("head", "ear"),
c("head", "hair"),
c("head", "forehead"),
c("head", "eyebrow"),
c("head", "eyebrows"),
c("head", "mouth"),
c("head", "eye"),
c("heard", "seen"),
c("heard", "tasted"),
c("heard", "smelled"),
c("heard", "saw"),
c("heard", "touched"),
c("heard", "listened"),
c("heard", "spoke"),
c("heard", "uttered"),
c("heard", "said"),
c("heart", "bosom"),
c("heart", "breast"),
c("heart", "chest"),
c("heart", "soul"),
c("heart", "mind"),
c("heart", "spirit"),
c("hearts", "souls"),
c("hearts", "minds"),
c("hearts", "bosoms"),
c("hearts", "breasts"),
c("heaven", "god"),
c("heaven", "almighty"),
c("heaven", "angels"),
c("heaven", "seraphs"),
c("heaven", "providence"),
c("heaven", "hell"),
c("heaven", "earth"),
c("heaven", "purgatory"),
c("help", "assist"),
c("help", "assistance"),
c("high", "low"),
c("high", "tall"),
c("high", "exalted"),
c("high", "lofty"),
c("high", "elevated"),
c("high", "towering"),
c("history", "biography"),
c("history", "chronology"),
c("history", "narrative"),
c("history", "story"),
c("history", "topography"),
c("history", "genealogy"),
c("history", "memoir"),
c("history", "memoirs"),
c("history", "compendium"),
c("history", "antiquities"),
c("home", "abroad"),
c("home", "house"),
c("home", "cottage"),
c("home", "mansion"),
c("home", "castle"),
c("home", "villa"),
c("honest", "dishonest"),
c("honest", "false"),
c("honest", "insincere"),
c("honest", "deceitful"),
c("honest", "untrue"),
c("honest", "deceptive"),
c("honest", "deceiving"),
c("honest", "counterfeit"),
c("honest", "spurious"),
c("honest", "calumnious"),
c("honest", "true"),
c("honest", "truthful"),
c("honest", "sincere"),
c("honor", "reputation"),
c("honor", "virtue"),
c("honor", "loyalty"),
c("honor", "probity"),
c("honor", "dignity"),
c("honor", "glory"),
c("honor", "renown"),
c("honor", "fame"),
c("hope", "wish"),
c("hope", "desire"),
c("hope", "expectation"),
c("hope", "expectance"),
c("hope", "trust"),
c("hope", "doubt"),
c("hope", "fear"),
c("hopes", "expectations"),
c("hopes", "wishes"),
c("hopes", "anticipations"),
c("hopes", "fears"),
c("hopes", "doubts"),
c("horse", "mule"),
c("horse", "pony"),
c("horse", "ox"),
c("horse", "steed"),
c("horse", "donkey"),
c("horse", "saddle"),
c("horse", "bridle"),
c("horse", "stirrup"),
c("horse", "stirrups"),
c("horse", "harness"),
c("horse", "horseman"),
c("horse", "rider"),
c("horse", "horsemen"),
c("horse", "buggy"),
c("horse", "cart"),
c("horse", "coach"),
c("horse", "wagon"),
c("horse", "waggon"),
c("horse", "curricule"),
c("horse", "hack"),
c("horse", "stable"),
c("horse", "barn"),
c("horses", "mules"),
c("horses", "oxen"),
c("horses", "ponies"),
c("horses", "cattle"),
c("horses", "dogs"),
c("horses", "cows"),
c("horses", "camels"),
c("horses", "wagons"),
c("horses", "carriages"),
c("horses", "buggies"),
c("horses", "chaises"),
c("horses", "postchaises"),
c("hour", "day"),
c("hour", "night"),
c("hour", "noon"),
c("hour", "midnight"),
c("hour", "morning"),
c("hour", "evening"),
c("hour", "minute"),
c("hour", "second"),
c("hour", "instant"),
c("hour", "week"),
c("hour", "year"),
c("house", "town"),
c("house", "city"),
c("house", "neighborhood"),
c("house", "cabin"),
c("house", "cottage"),
c("house", "manor"),
c("house", "mansion"),
c("house", "shanty"),
c("house", "parsonage"),
c("house", "barn"),
c("house", "apartment"),
c("house", "apartments"),
c("house", "shanty"),
c("house", "parlour"),
c("house", "parlor"),
c("house", "bedroom"),
c("house", "room"),
c("house", "kitchen"),
c("house", "stateroom"),
c("house", "laundry"),
c("house", "hall"),
c("house", "lobby"),
c("house", "cellar"),
c("house", "basement"),
c("house", "garrett"),
c("houses", "cabins"),
c("houses", "cottages"),
c("houses", "farmhouses"),
c("houses", "hotels"),
c("houses", "taverns"),
c("houses", "chapels"),
c("houses", "warehouses"),
c("houses", "buildings"),
c("human", "animal"),
c("humble", "obedient"),
c("humble", "dutiful"),
c("humble", "lowly"),
c("humble", "submissive"),
c("idea", "notion"),
c("idea", "conception"),
c("idea", "concept"),
c("idea", "conception"),
c("idea", "feeling"),
c("ideas", "perceptions"),
c("ideas", "conceptions"),
c("ideas", "thoughts"),
c("ideas", "notions"),
c("ideas", "sentiments"),
c("influence", "ascendancy"),
c("influence", "power"),
c("influence", "authority"),
c("influence", "control"),
c("influence", "agency"),
c("informed", "told"),
c("informed", "apprised"),
c("informed", "apprized"),
c("joy", "gladness"),
c("joy", "rapture"),
c("joy", "ecstasy"),
c("joy", "delight"),
c("joy", "pleasure"),
c("joy", "happiness"),
c("joy", "bliss"),
c("joy", "sadness"),
c("joy", "sorrow"),
c("joy", "grief"),
c("joy", "anguish"),
c("joy", "woe"),
c("judge", "jury"),
c("judge", "lawyer"),
c("justice", "equity"),
c("justice", "humanity"),
c("justice", "fairness"),
c("justice", "impartiality"),
c("justice", "honor"),
c("justice", "uprightness"),
c("justice", "evenhandedness"),
c("justice", "injustice"),
c("justice", "unfairness"),
c("kind", "sort"),
c("kind", "friendly"),
c("kind", "helpful"),
c("kind", "compassionate"),
c("kind", "bountiful"),
c("king", "prince"),
c("king", "monarch"),
c("king", "queen"),
c("king", "princess"),
c("king", "emperor"),
c("king", "emperours"),
c("king", "regent"),
c("king", "sovereign"),
c("king", "throne"),
c("king", "crown"),
c("kingdom", "nation"),
c("kingdom", "empire"),
c("kingdom", "dominion"),
c("kingdom", "country"),
c("kingdom", "principality"),
c("kingdom", "realm"),
c("kingdom", "province"),
c("kingdom", "commonwealth"),
c("kingdom", "territory"),
c("kingdom", "fiefdom"),
c("know", "think"),
c("know", "understand"),
c("know", "believe"),
c("know", "remember"),
c("knowledge", "learning"),
c("knowledge", "understanding"),
c("knowledge", "acquirement"),
c("knowledge", "scholarship"),
c("knowledge", "study"),
c("knowledge", "improvement"),
c("knowledge", "instruction"),
c("knowledge", "teaching"),
c("knowledge", "experience"),
c("knows", "realizes"),
c("knows", "thinks"),
c("knows", "understands"),
c("knows", "believes"),
c("labor", "toil"),
c("labor", "work"),
c("labor", "drudgery"),
c("labor", "employment"),
c("labor", "industry"),
c("lady", "countess"),
c("lady", "marchioness"),
c("lady", "duchess"),
c("lady", "baroness"),
c("lady", "marquise"),
c("lady", "viscountess"),
c("land", "country"),
c("land", "kingdom"),
c("land", "domain"),
c("land", "ground"),
c("land", "soil"),
c("land", "earth"),
c("land", "plains"),
c("land", "coast"),
c("land", "fields"),
c("land", "shore"),
c("land", "desert"),
c("land", "tract"),
c("land", "wilderness"),
c("lands", "manors"),
c("lands", "estates"),
c("lands", "farms"),
c("lands", "domains"),
c("lands", "territories"),
c("language", "dialect"),
c("language", "vernacular"),
c("language", "phrase"),
c("language", "phrases"),
c("language", "word"),
c("language", "words"),
c("language", "vocabulary"),
c("language", "idom"),
c("language", "idioms"),
c("language", "orthography"),
c("language", "pronunciation"),
c("large", "small"),
c("large", "tiny"),
c("large", "little"),
c("large", "big"),
c("large", "huge"),
c("large", "considerable"),
c("large", "vast"),
c("large", "roomy"),
c("last", "first"),
c("late", "early"),
c("laws", "rules"),
c("laws", "policies"),
c("laws", "bylaws"),
c("laws", "sanctions"),
c("laws", "violations"),
c("laws", "enforcement"),
c("learn", "teach"),
c("learn", "instruct"),
c("learn", "appreciate"),
c("learn", "know"),
c("learn", "understand"),
c("learning", "erudition"),
c("learning", "education"),
c("learning", "knowledge"),
c("learning", "proficiency"),
c("learning", "scholarship"),
c("least", "most"),
c("least", "smallest"),
c("least", "slightest"),
c("least", "merest"),
c("less", "more"),
c("less", "greater"),
c("less", "oftener"),
c("less", "longer"),
c("liberty", "freedom"),
c("liberty", "independence"),
c("lies", "stands"),
c("lies", "rests"),
c("lies", "remains"),
c("life", "death"),
c("life", "existence"),
c("light", "dark"),
c("light", "dim"),
c("light", "gloom"),
c("light", "beam"),
c("light", "beams"),
c("light", "sunlight"),
c("light", "ray"),
c("light", "rays"),
c("light", "sunbeam"),
c("light", "sunbeams"),
c("light", "radiance"),
c("light", "brightness"),
c("light", "sun"),
c("likewise", "also"),
c("likewise", "similarly"),
c("likewise", "nevertheless"),
c("likewise", "indeed"),
c("likewise", "besides"),
c("likewise", "whereas"),
c("likewise", "moreover"),
c("lines", "verses"),
c("lines", "stanzas"),
c("lines", "couplet"),
c("lines", "couplets"),
c("lines", "pages"),
c("lines", "words"),
c("lines", "passages"),
c("little", "big"),
c("little", "large"),
c("little", "huge"),
c("little", "small"),
c("little", "tiny"),
c("live", "remain"),
c("live", "subsist"),
c("live", "dwell"),
c("live", "reside"),
c("live", "survive"),
c("live", "stay"),
c("live", "die"),
c("lived", "resided"),
c("lived", "stayed"),
c("lived", "remained"),
c("lived", "staid"),
c("lived", "sojourned"),
c("lived", "dwelt"),
c("lived", "subsisted"),
c("lived", "cohabited"),
c("long", "short"),
c("long", "brief"),
c("long", "protracted"),
c("look", "stare"),
c("look", "spy"),
c("look", "squint"),
c("look", "eye"),
c("look", "glance"),
c("look", "gaze"),
c("looks", "face"),
c("looks", "appearance"),
c("looks", "countenance"),
c("lords", "peers"),
c("lords", "mayors"),
c("lords", "kings"),
c("lords", "elders"),
c("lords", "barons"),
c("lords", "judges"),
c("lords", "nobles"),
c("lords", "bishops"),
c("lords", "prelates"),
c("lords", "justices"),
c("lost", "found"),
c("lost", "regained"),
c("lost", "gained"),
c("lost", "forgot"),
c("love", "hate"),
c("love", "friendship"),
c("loved", "lovd"),
c("loved", "beloved"),
c("loved", "adored"),
c("loved", "idolized"),
c("loved", "respected"),
c("loved", "sympathized"),
c("loved", "sympathised"),
c("loved", "hated"),
c("low", "high"),
c("low", "lofty"),
c("maid", "maiden"),
c("maid", "damsel"),
c("majesty", "highness"),
c("majesty", "sovereign"),
c("majesty", "lordship"),
c("majesty", "king"),
c("majesty", "queen"),
c("majesty", "empress"),
c("majesty", "emperor"),
c("majesty", "prince"),
c("majesty", "princess"),
c("man", "creature"),
c("man", "person"),
c("man", "boy"),
c("man", "woman"),
c("manner", "mode"),
c("manner", "style"),
c("manner", "method"),
c("manners", "habits"),
c("manners", "customs"),
c("manners", "behavior"),
c("manners", "deportment"),
c("manners", "morals"),
c("manners", "politeness"),
c("manners", "refinement"),
c("manners", "gentleness"),
c("marriage", "divorce"),
c("marriage", "nuptials"),
c("marriage", "banns"),
c("marriage", "wedlock"),
c("marriage", "matrimony"),
c("marriage", "wedlock"),
c("marriage", "wife"),
c("marriage", "husband"),
c("marriage", "spouse"),
c("matter", "question"),
c("matter", "subject"),
c("matter", "substance"),
c("mean", "intend"),
c("mean", "propose"),
c("mean", "think"),
c("mean", "signify"),
c("memory", "recollection"),
c("memory", "remembrances"),
c("men", "people"),
c("men", "women"),
c("men", "persons"),
c("men", "fellows"),
c("men", "citizens"),
c("men", "folks"),
c("men", "women"),
c("mention", "remark"),
c("mention", "relate"),
c("mentioned", "alluded"),
c("mentioned", "hinted"),
c("mentioned", "observed"),
c("mentioned", "described"),
c("mentioned", "noticed"),
c("mentioned", "noted"),
c("mentioned", "stated"),
c("mentioned", "remarked"),
c("mentioned", "intimated"),
c("mercy", "justice"),
c("mercy", "compassion"),
c("mercy", "pardoning"),
c("mercy", "clemency"),
c("merit", "excellence"),
c("merit", "talents"),
c("merit", "originality"),
c("merit", "attainments"),
c("might", "could"),
c("might", "may"),
c("might", "seemed"),
c("might", "should"),
c("might", "must"),
c("miles", "leagues"),
c("miles", "yards"),
c("mind", "imagination"),
c("mind", "thoughts"),
c("mind", "intellect"),
c("mind", "ideas"),
c("mind", "fancy"),
c("mind", "feelings"),
c("mind", "feeling"),
c("mind", "sensibilities"),
c("mind", "senses"),
c("mind", "sense"),
c("mind", "soul"),
c("mind", "heart"),
c("mind", "bosom"),
c("mind", "brain"),
c("minds", "hearts"),
c("minds", "souls"),
c("mistress", "husband"),
c("mistress", "wife"),
c("mistress", "master"),
c("mistress", "aunt"),
c("mistress", "sister"),
c("mistress", "godmother"),
c("mistress", "mother"),
c("mistress", "niece"),
c("mistress", "cousin"),
c("moment", "instant"),
c("moment", "minute"),
c("moment", "hour"),
c("moment", "second"),
c("moment", "pause"),
c("money", "cash"),
c("money", "funds"),
c("money", "fund"),
c("money", "currency"),
c("money", "refund"),
c("money", "discount"),
c("money", "mortgage"),
c("money", "drafts"),
c("money", "sums"),
c("money", "purchase"),
c("money", "remittance"),
c("money", "mortgages"),
c("money", "debts"),
c("money", "wages"),
c("money", "stock"),
c("money", "savings"),
c("money", "investments"),
c("money", "credit"),
c("money", "purse"),
c("money", "borrowers"),
c("money", "lenders"),
c("months", "years"),
c("months", "days"),
c("months", "hours"),
c("months", "fortnights"),
c("morning", "night"),
c("morning", "twilight"),
c("morning", "afternoon"),
c("morning", "dusk"),
c("morning", "evening"),
c("morning", "forenoon"),
c("morning", "sunrise"),
c("morning", "daybreak"),
c("morning", "noon"),
c("morning", "midday"),
c("morning", "sunset"),
c("morning", "day"),
c("mother", "father"),
c("mother", "child"),
c("mother", "daughter"),
c("mother", "son"),
c("mother", "baby"),
c("mother", "babe"),
c("mother", "aunt"),
c("mother", "uncle"),
c("mother", "grandfather"),
c("mother", "grandmother"),
c("mother", "grandparent"),
c("mother", "grandson"),
c("mother", "granddaughter"),
c("mother", "grandchild"),
c("mother", "niece"),
c("mother", "nephew"),
c("mother", "wife"),
c("mother", "parent"),
c("mountains", "hills"),
c("mountains", "cliffs"),
c("mountains", "summits"),
c("mountains", "valleys"),
c("mouth", "ears"),
c("mouth", "eyes"),
c("mouth", "nose"),
c("mouth", "tongue"),
c("mouth", "lips"),
c("mouth", "throat"),
c("mr", "mrs"),
c("mr", "miss"),
c("mr", "mister"),
c("mr", "rev"),
c("mr", "reverend"),
c("mr", "sir"),
c("mr", "dr"),
c("mr", "doctor"),
c("music", "melody"),
c("music", "harmony"),
c("name", "appellation"),
c("name", "surname"),
c("name", "title"),
c("nation", "republic"),
c("nation", "kingdom"),
c("nation", "commonwealth"),
c("nation", "monarchy"),
c("nation", "government"),
c("near", "far"),
c("near", "distant"),
c("near", "close"),
c("near", "proximate"),
c("neither", "nor"),
c("neither", "either"),
c("neither", "hardly"),
c("neither", "scarce"),
c("neither", "seldom"),
c("neither", "nothing"),
c("neither", "never"),
c("neither", "any"),
c("neither", "scarcely"),
c("never", "always"),
c("never", "constantly"),
c("never", "invariably"),
c("never", "often"),
c("never", "frequently"),
c("never", "scarcely"),
c("never", "hardly"),
c("new", "fresh"),
c("new", "old"),
c("next", "first"),
c("next", "last"),
c("next", "second"),
c("next", "third"),
c("next", "fourth"),
c("next", "fifth"),
c("next", "immediately"),
c("next", "soon"),
c("night", "day"),
c("night", "morning"),
c("night", "noon"),
c("night", "sunrise"),
c("night", "afternoon"),
c("night", "evening"),
c("night", "dusk"),
c("night", "nightfall"),
c("night", "twilight"),
c("night", "midnight"),
c("night", "starlight"),
c("noble", "valorous"),
c("noble", "virtuous"),
c("noble", "dignified"),
c("noble", "worthy"),
c("noble", "valiant"),
c("noble", "brave"),
c("noble", "heroic"),
c("none", "never"),
c("none", "neither"),
c("none", "nobody"),
c("none", "nothing"),
c("none", "hardly"),
c("none", "alone"),
c("nothing", "something"),
c("nothing", "anything"),
c("nothing", "thing"),
c("nothing", "everything"),
c("nothing", "naught"),
c("nothing", "none"),
c("nothing", "nobody"),
c("nothing", "never"),
c("nothing", "nowhere"),
c("notwithstanding", "nevertheless"),
c("notwithstanding", "indeed"),
c("notwithstanding", "however"),
c("notwithstanding", "although"),
c("obliged", "compelled"),
c("obliged", "forced"),
c("obliged", "required"),
c("obliged", "necessitated"),
c("obliged", "induced"),
c("observe", "perceive"),
c("obtained", "procured"),
c("obtained", "gained"),
c("obtained", "received"),
c("obtained", "purchased"),
c("obtained", "acquired"),
c("obtained", "secured"),
c("occasion", "occurrence"),
c("occasion", "instance"),
c("offered", "accepted"),
c("offered", "refused"),
c("offered", "tendered"),
c("offered", "promised"),
c("offered", "volunteered"),
c("officers", "privates"),
c("officers", "sergeants"),
c("officers", "lieutenants"),
c("officers", "generals"),
c("officers", "captains"),
c("officers", "corporals"),
c("officers", "soldiers"),
c("officers", "deputies"),
c("officers", "yeoman"),
c("officers", "constables"),
c("officers", "regulars"),
c("officers", "police"),
c("officers", "commanders"),
c("officers", "marines"),
c("officers", "constables"),
c("old", "elderly"),
c("old", "aged"),
c("old", "young"),
c("old", "sprightly"),
c("old", "gawky"),
c("old", "youthful"),
c("old", "new"),
c("old", "fresh"),
c("old", "grandfather"),
c("old", "grandmother"),
c("old", "invalid"),
c("open", "shut"),
c("open", "closed"),
c("open", "bolted"),
c("open", "unlocked"),
c("opinion", "thought"),
c("opinion", "notion"),
c("opinion", "conception"),
c("opinion", "supposition"),
c("opinion", "theory"),
c("order", "disorder"),
c("order", "chaos"),
c("order", "instruct"),
c("order", "command"),
c("order", "direct"),
c("order", "request"),
c("order", "instruction"),
c("order", "command"),
c("orders", "instructions"),
c("orders", "dispatches"),
c("orders", "commissions"),
c("orders", "injunctions"),
c("orders", "directions"),
c("orders", "appointments"),
c("orders", "commands"),
c("pain", "anguish"),
c("pain", "grief"),
c("pain", "pangs"),
c("pain", "sorrow"),
c("pain", "agony"),
c("paper", "parchment"),
c("paper", "newspaper"),
c("paper", "pamphlet"),
c("paper", "document"),
c("pardon", "forgiveness"),
c("pardon", "beg"),
c("pardon", "plead"),
c("pardon", "intreat"),
c("pardon", "apologize"),
c("pardon", "apologise"),
c("pardon", "entreat"),
c("parents", "mothers"),
c("parents", "fathers"),
c("parents", "children"),
c("parents", "grandparents"),
c("parents", "grandchildren"),
c("parents", "sisters"),
c("parents", "brothers"),
c("parents", "husbands"),
c("parents", "wives"),
c("parents", "grandmothers"),
c("parents", "grandfathers"),
c("part", "portion"),
c("part", "whole"),
c("passion", "affection"),
c("passion", "fondness"),
c("passion", "ambition"),
c("passion", "ardency"),
c("passion", "excess"),
c("passion", "desire"),
c("past", "present"),
c("past", "future"),
c("pay", "refund"),
c("pay", "disburse"),
c("pay", "reimburse"),
c("pay", "discount"),
c("pay", "purchase"),
c("pay", "buy"),
c("pay", "money"),
c("pay", "moneys"),
c("pay", "wages"),
c("pay", "funds"),
c("pay", "tithe"),
c("pay", "debts"),
c("pay", "fees"),
c("pay", "mortgage"),
c("pay", "cash"),
c("peace", "tranquility"),
c("peace", "quietness"),
c("peace", "tranquillity"),
c("peace", "quietude"),
c("peace", "quiet"),
c("peace", "contentment"),
c("peace", "amity"),
c("peace", "calm"),
c("people", "men"),
c("people", "women"),
c("people", "citizens"),
c("people", "inhabitants"),
c("people", "members"),
c("perfect", "complete"),
c("perfect", "absolute"),
c("perfect", "inimitable"),
c("perfect", "compleatest"),
c("perfect", "unalloyed"),
c("perfectly", "thoroughly"),
c("perfectly", "completely"),
c("perfectly", "entirely"),
c("perhaps", "probably"),
c("perhaps", "possibly"),
c("perhaps", "likely"),
c("perhaps", "certainly"),
c("perhaps", "doubtless"),
c("perhaps", "surely"),
c("period", "epoch"),
c("period", "interval"),
c("period", "duration"),
c("period", "phase"),
c("period", "era"),
c("period", "æra"),
c("period", "age"),
c("period", "decade"),
c("period", "century"),
c("period", "time"),
c("person", "man"),
c("person", "woman"),
c("person", "gentleman"),
c("person", "gentlewoman"),
c("person", "boy"),
c("person", "girl"),
c("person", "child"),
c("person", "individual"),
c("person", "personage"),
c("pity", "compassion"),
c("pity", "sympathy"),
c("pity", "commiseration"),
c("plain", "simple"),
c("plain", "clear"),
c("plain", "obvious"),
c("plain", "greensward"),
c("plain", "prairie"),
c("plain", "ground"),
c("plain", "lawn"),
c("play", "dance"),
c("play", "sport"),
c("play", "merrymaking"),
c("play", "frolic"),
c("play", "gambols"),
c("play", "gambol"),
c("play", "romps"),
c("pleased", "delighted"),
c("pleased", "satisfied"),
c("pleased", "contented"),
c("pleased", "overjoyed"),
c("pleased", "displeased"),
c("pleasure", "delight"),
c("pleasure", "joy"),
c("pleasure", "satisfaction"),
c("pleasure", "happiness"),
c("pleasure", "felicity"),
c("pleasure", "ease"),
c("pleasure", "enjoyment"),
c("pleasure", "contentment"),
c("pleasure", "bliss"),
c("pleasure", "pain"),
c("poet", "satirist"),
c("poet", "bard"),
c("poet", "writer"),
c("poet", "poetess"),
c("poet", "composer"),
c("poor", "rich"),
c("poor", "wretched"),
c("poor", "helpless"),
c("poor", "distressed"),
c("poor", "miserable"),
c("poor", "friendless"),
c("poor", "unhappy"),
c("poor", "pitiful"),
c("poor", "forlorn"),
c("poor", "unfortunate"),
c("poor", "indigent"),
c("poor", "penniless"),
c("poor", "pennyless"),
c("poor", "impecunious"),
c("poor", "penurious"),
c("pounds", "dollars"),
c("pounds", "shillings"),
c("pounds", "guineas"),
c("pounds", "ducats"),
c("pounds", "rupees"),
c("pounds", "livres"),
c("pounds", "florins"),
c("pounds", "piastres"),
c("pounds", "piastoles"),
c("pounds", "guilders"),
c("power", "omnipotence"),
c("power", "potency"),
c("power", "authority"),
c("power", "influence"),
c("power", "sovereign"),
c("power", "sovereignty"),
c("power", "dominion"),
c("power", "agency"),
c("power", "control"),
c("powers", "strengths"),
c("powers", "faculties"),
c("powers", "capabilities"),
c("prevent", "avoid"),
c("prevent", "deter"),
c("prevent", "counteract"),
c("price", "rates"),
c("price", "rate"),
c("price", "cost"),
c("price", "premium"),
c("pride", "vanity"),
c("pride", "ambition"),
c("pride", "arrogance"),
c("pride", "vainglory"),
c("pride", "humility"),
c("prince", "king"),
c("prince", "queen"),
c("prince", "princess"),
c("prince", "duke"),
c("prince", "emperor"),
c("prince", "emperour"),
c("prince", "monarch"),
c("prince", "nobleman"),
c("principles", "fundamentals"),
c("principles", "maxims"),
c("principles", "tenets"),
c("principles", "doctrines"),
c("private", "public"),
c("private", "publick"),
c("private", "confidential"),
c("private", "personal"),
c("private", "domestic"),
c("private", "domestick"),
c("promise", "vow"),
c("promise", "pledge"),
c("proper", "fit"),
c("proper", "suitable"),
c("proper", "requisite"),
c("proper", "needful"),
c("proper", "necessary"),
c("proper", "sufficient"),
c("proper", "fitting"),
c("proper", "improper"),
c("proud", "haughty"),
c("proud", "ambitious"),
c("proud", "boastful"),
c("proud", "humble"),
c("prove", "demonstrate"),
c("prove", "verify"),
c("prove", "ensure"),
c("prove", "evince"),
c("prove", "confirm"),
c("prove", "disprove"),
c("prove", "falsify"),
c("proved", "disproved"),
c("public", "private"),
c("public", "domestic"),
c("public", "national"),
c("public", "society"),
c("public", "community"),
c("public", "popular"),
c("published", "republished"),
c("published", "revised"),
c("published", "reprinted"),
c("published", "printed"),
c("published", "compiled"),
c("published", "written"),
c("pure", "untainted"),
c("pure", "undefiled"),
c("pure", "unsullied"),
c("pure", "spotless"),
c("pure", "unadulterated"),
c("pure", "immaculate"),
c("pure", "unstained"),
c("purpose", "design"),
c("purpose", "plan"),
c("purpose", "intention"),
c("put", "carry"),
c("put", "set"),
c("put", "stow"),
c("put", "fasten"),
c("put", "bundle"),
c("question", "dispute"),
c("question", "debate"),
c("question", "deliberate"),
c("question", "query"),
c("question", "answer"),
c("rage", "fury"),
c("rage", "anger"),
c("rage", "frenzy"),
c("rage", "rancour"),
c("rage", "rancor"),
c("raise", "lift"),
c("raise", "ascend"),
c("read", "write"),
c("read", "book"),
c("read", "peruse"),
c("read", "study"),
c("reader", "editor"),
c("reader", "publisher"),
c("reader", "author"),
c("reader", "writer"),
c("reader", "compiler"),
c("real", "imaginary"),
c("real", "fake"),
c("real", "fictitious"),
c("real", "actual"),
c("real", "uncontested"),
c("religion", "christianity"),
c("religion", "protestantism"),
c("religion", "catholicism"),
c("religion", "paganism"),
c("religion", "judaism"),
c("religion", "polytheism"),
c("religion", "theism"),
c("religion", "faith"),
c("religion", "morality"),
c("religion", "ritual"),
c("religion", "doctrine"),
c("religion", "tenets"),
c("religion", "institutions"),
c("religion", "beliefs"),
c("religion", "believer"),
c("religion", "church"),
c("religion", "churches"),
c("religion", "temple"),
c("religion", "temples"),
c("religion", "synagogue"),
c("religion", "synagogues"),
c("remained", "stayed"),
c("remained", "staid"),
c("remained", "tarried"),
c("remained", "continued"),
c("remained", "lingered"),
c("remained", "resided"),
c("remarkable", "singular"),
c("remarkable", "extraordinary"),
c("remarkable", "uncommon"),
c("remarkable", "striking"),
c("remarkable", "conspicuous"),
c("remarkable", "noticeable"),
c("remember", "recollect"),
c("remember", "recall"),
c("remember", "forget"),
c("respect", "reverence"),
c("respect", "esteem"),
c("respect", "honor"),
c("respect", "honour"),
c("respect", "worthiness"),
c("rest", "repose"),
c("rest", "sleep"),
c("rest", "slumber"),
c("rest", "quietude"),
c("rest", "quiet"),
c("return", "arrival"),
c("return", "departure"),
c("rich", "wealthy"),
c("rich", "expensive"),
c("rich", "luxurious"),
c("rich", "costly"),
c("rich", "fine"),
c("right", "wrong"),
c("rise", "descend"),
c("rise", "fall"),
c("rise", "raise"),
c("rise", "arise"),
c("rise", "ascend"),
c("rise", "swell"),
c("rise", "lift"),
c("river", "lake"),
c("river", "ocean"),
c("river", "creek"),
c("river", "stream"),
c("road", "turnpike"),
c("road", "highroad"),
c("road", "path"),
c("road", "highway"),
c("road", "footpath"),
c("road", "track"),
c("roman", "grecian"),
c("roman", "athenian"),
c("roman", "macedonian"),
c("roman", "saxon"),
c("roman", "persian"),
c("roman", "emperors"),
c("rome", "athens"),
c("rome", "carthage"),
c("rome", "constantinople"),
c("rome", "sparta"),
c("rome", "thebes"),
c("rome", "corinth"),
c("room", "parlor"),
c("room", "parlour"),
c("room", "chamber"),
c("room", "apartment"),
c("room", "bedroom"),
c("room", "kitchen"),
c("room", "closet"),
c("room", "antichamber"),
c("room", "refectory"),
c("room", "lobby"),
c("room", "bedchamber"),
c("room", "garret"),
c("room", "storeroom"),
c("room", "laundry"),
c("room", "salon"),
c("room", "gallery"),
c("room", "house"),
c("room", "cabin"),
c("room", "mansion"),
c("room", "window"),
c("room", "table"),
c("room", "cupboard"),
c("room", "drawer"),
c("room", "chair"),
c("room", "chairs"),
c("room", "bed"),
c("room", "fireplace"),
c("room", "balcony"),
c("room", "bedstead"),
c("room", "stove"),
c("rule", "law"),
c("rule", "precept"),
c("rule", "commandment"),
c("sacred", "hallowed"),
c("sacred", "holy"),
c("sacred", "holiest"),
c("sacred", "consecrated"),
c("sacred", "unholy"),
c("sacred", "unhallowed"),
c("sacred", "unconsecrated"),
c("sacred", "profane"),
c("sad", "mournful"),
c("sad", "melancholy"),
c("sad", "dismal"),
c("sad", "sorrowful"),
c("sad", "doleful"),
c("sad", "woeful"),
c("sad", "happy"),
c("sad", "glad"),
c("sad", "joyful"),
c("save", "redeem"),
c("save", "rescue"),
c("save", "spare"),
c("save", "protect"),
c("save", "preserve"),
c("say", "know"),
c("say", "think"),
c("say", "believe"),
c("say", "remember"),
c("say", "swear"),
c("say", "affirm"),
c("say", "call"),
c("say", "tell"),
c("say", "avouch"),
c("say", "speak"),
c("say", "declare"),
c("school", "boarding"),
c("school", "seminary"),
c("school", "institute"),
c("school", "university"),
c("school", "academy"),
c("school", "college"),
c("school", "day"),
c("school", "sunday"),
c("school", "students"),
c("school", "teacher"),
c("school", "education"),
c("school", "training"),
c("sea", "ocean"),
c("sea", "atlantic"),
c("sea", "mediterranean"),
c("sea", "caspian"),
c("sea", "baltic"),
c("sea", "adriatic"),
c("sea", "lake"),
c("sea", "river"),
c("sea", "shoal"),
c("sea", "coast"),
c("sea", "surf"),
c("sea", "water"),
c("sea", "waters"),
c("secret", "hidden"),
c("secret", "concealed"),
c("secret", "mysterious"),
c("see", "look"),
c("see", "view"),
c("see", "behold"),
c("see", "notice"),
c("see", "espy"),
c("see", "hear"),
c("see", "taste"),
c("see", "touch"),
c("see", "smell"),
c("seldom", "rarely"),
c("seldom", "scarcely"),
c("seldom", "frequently"),
c("seldom", "usually"),
c("seldom", "generally"),
c("seldom", "often"),
c("seldom", "commonly"),
c("sense", "feeling"),
c("sense", "sentiment"),
c("sense", "understanding"),
c("sense", "perception"),
c("sensible", "insensible"),
c("sentiments", "feelings"),
c("sentiments", "opinions"),
c("sentiments", "ideas"),
c("sentiments", "principles"),
c("sentiments", "emotions"),
c("sentiments", "motives"),
c("servant", "butler"),
c("servant", "maid"),
c("servant", "housekeeper"),
c("servant", "scullion"),
c("servant", "chambermaid"),
c("servant", "coachman"),
c("servant", "valet"),
c("servant", "footman"),
c("service", "offices"),
c("service", "work"),
c("service", "duty"),
c("service", "employment"),
c("several", "diverse"),
c("several", "various"),
c("several", "different"),
c("several", "sundry"),
c("sex", "gender"),
c("ship", "boat"),
c("ship", "vessel"),
c("ship", "berth"),
c("ship", "port"),
c("ship", "dock"),
c("ship", "harbour"),
c("ship", "wharf"),
c("ship", "harbor"),
c("ship", "sloop"),
c("ship", "privateer"),
c("ship", "frigate"),
c("ship", "canoe"),
c("ship", "privateer"),
c("ship", "longboat"),
c("ship", "steamboat"),
c("ship", "steamer"),
c("ship", "galleon"),
c("ship", "anchors"),
c("ship", "rigging"),
c("ship", "sails"),
c("ship", "masts"),
c("ship", "sail"),
c("ship", "anchor"),
c("ship", "mast"),
c("ships", "boats"),
c("ships", "vessels"),
c("ships", "frigates"),
c("ships", "privateers"),
c("ships", "merchantmen"),
c("ships", "sloops"),
c("ships", "canoes"),
c("ships", "galleons"),
c("ships", "schooners"),
c("ships", "steamboats"),
c("ships", "steamers"),
c("ships", "anchors"),
c("ships", "rigging"),
c("ships", "sails"),
c("ships", "masts"),
c("ships", "sail"),
c("ships", "anchor"),
c("ships", "mast"),
c("ships", "seamen"),
c("ships", "crews"),
c("ships", "sailors"),
c("ships", "fleets"),
c("ships", "convoys"),
c("ships", "ports"),
c("ships", "docks"),
c("ships", "harbours"),
c("ships", "harbors"),
c("shore", "coast"),
c("shore", "beach"),
c("shore", "sands"),
c("shore", "headland"),
c("shore", "shoal"),
c("short", "brief"),
c("short", "slight"),
c("short", "small"),
c("short", "lengthy"),
c("short", "long"),
c("side", "top"),
c("side", "bottom"),
c("side", "head"),
c("side", "front"),
c("side", "back"),
c("side", "foot"),
c("silence", "stillness"),
c("silent", "loud"),
c("silent", "mute"),
c("silent", "hushed"),
c("silent", "speechless"),
c("silent", "hushed"),
c("sit", "stand"),
c("sit", "walk"),
c("sit", "jog"),
c("sit", "lie"),
c("sit", "kneel"),
c("situation", "condition"),
c("situation", "circumstances"),
c("situation", "surroundings"),
c("situation", "state"),
c("situation", "location"),
c("situation", "position"),
c("sleep", "slumber"),
c("sleep", "repose"),
c("sleep", "doze"),
c("sleep", "bed"),
c("sleep", "pillow"),
c("sleep", "couch"),
c("sleep", "night"),
c("sleep", "midnight"),
c("small", "large"),
c("small", "vast"),
c("small", "enormous"),
c("small", "considerable"),
c("small", "big"),
c("small", "huge"),
c("small", "little"),
c("small", "tiny"),
c("society", "community"),
c("society", "association"),
c("society", "connections"),
c("society", "connexions"),
c("sold", "bought"),
c("sold", "bargained"),
c("sold", "purchased"),
c("sold", "mortgaged"),
c("sold", "appraised"),
c("sold", "owned"),
c("sometimes", "frequently"),
c("sometimes", "often"),
c("sometimes", "generally"),
c("sometimes", "always"),
c("sometimes", "usually"),
c("sometimes", "occasionally"),
c("sometimes", "constantly"),
c("sometimes", "rarely"),
c("sometimes", "commonly"),
c("sometimes", "oftentimes"),
c("son", "father"),
c("son", "mother"),
c("son", "aunt"),
c("son", "uncle"),
c("son", "grandfather"),
c("son", "grandmother"),
c("son", "grandparent"),
c("son", "daughter"),
c("son", "child"),
c("son", "stepson"),
c("son", "stepdaughter"),
c("son", "nephew"),
c("son", "niece"),
c("son", "grandson"),
c("son", "grandfather"),
c("son", "grandchild"),
c("song", "ditty"),
c("song", "tune"),
c("song", "dirge"),
c("song", "lullaby"),
c("song", "carol"),
c("song", "chaunt"),
c("song", "chant"),
c("sons", "fathers"),
c("sons", "daughters"),
c("sons", "sisters"),
c("sons", "mothers"),
c("sons", "brothers"),
c("sons", "sires"),
c("sons", "progenitors"),
c("sons", "grandsons"),
c("sons", "granddaughters"),
c("sons", "grandchildren"),
c("sons", "offspring"),
c("sons", "children"),
c("sons", "descendants"),
c("soon", "quickly"),
c("soon", "shortly"),
c("soon", "presently"),
c("soon", "immediately"),
c("soon", "speedily"),
c("soon", "suddenly"),
c("sorrow", "joy"),
c("sorrow", "misery"),
c("sorrow", "grief"),
c("sorrow", "anguish"),
c("sorrow", "woe"),
c("sorrow", "sadness"),
c("sorrow", "affliction"),
c("speak", "talk"),
c("speak", "explain"),
c("speak", "declare"),
c("speak", "say"),
c("speak", "tell"),
c("speak", "listen"),
c("speak", "hear"),
c("speech", "utterance"),
c("speech", "address"),
c("speech", "discourse"),
c("speech", "reply"),
c("speech", "declaration"),
c("spirit", "soul"),
c("spoke", "uttered"),
c("spoke", "talked"),
c("spoke", "whispered"),
c("spoke", "stated"),
c("spoke", "heard"),
c("spoke", "listened"),
c("spring", "winter"),
c("spring", "summer"),
c("spring", "autumn"),
c("spring", "season"),
c("states", "governments"),
c("states", "legislatures"),
c("states", "departments"),
c("stone", "marble"),
c("stone", "gravel"),
c("stone", "chalk"),
c("stone", "slate"),
c("stone", "brick"),
c("stone", "bricks"),
c("stone", "slab"),
c("stone", "slabs"),
c("stone", "rock"),
c("stone", "quarry"),
c("stone", "quarries"),
c("story", "tale"),
c("story", "history"),
c("story", "narrative"),
c("story", "recital"),
c("story", "anecdote"),
c("story", "episode"),
c("story", "narration"),
c("story", "fable"),
c("strange", "unaccountable"),
c("strange", "odd"),
c("strange", "surprizing"),
c("strange", "surprising"),
c("strange", "wonderful"),
c("strength", "vigor"),
c("strength", "vigour"),
c("strength", "force"),
c("strength", "firmness"),
c("strength", "courage"),
c("strength", "hardiness"),
c("strength", "energy"),
c("strength", "agility"),
c("strength", "fortitude"),
c("strength", "weakness"),
c("strength", "feebleness"),
c("strong", "weak"),
c("strong", "slight"),
c("strong", "powerful"),
c("strong", "vigorous"),
c("strong", "firm"),
c("strong", "irresistible"),
c("strong", "stout"),
c("subject", "topic"),
c("sudden", "unforeseen"),
c("sudden", "unexpected"),
c("suffered", "endured"),
c("suffered", "underwent"),
c("sufficient", "necessary"),
c("sufficient", "requisite"),
c("sufficient", "enough"),
c("sufficient", "adequate"),
c("sufficient", "proper"),
c("sufficient", "needful"),
c("sufficient", "proportionate"),
c("sufficient", "insufficient"),
c("sufficient", "inadequate"),
c("sum", "amount"),
c("sum", "dividend"),
c("sum", "payment"),
c("sum", "premium"),
c("sum", "loan"),
c("sum", "investment"),
c("sun", "sky"),
c("sun", "skies"),
c("sun", "firmament"),
c("sun", "horizon"),
c("sun", "moon"),
c("sun", "light"),
c("sun", "beams"),
c("sun", "rays"),
c("sun", "brightness"),
c("sun", "beam"),
c("sun", "sunlight"),
c("sun", "star"),
c("sun", "day"),
c("sun", "noon"),
c("sun", "noonday"),
c("sun", "morning"),
c("superior", "inferior"),
c("superior", "preeminent"),
c("superior", "excelling"),
c("superior", "surpassing"),
c("superior", "unrivalled"),
c("superior", "uncontested"),
c("superior", "unrivaled"),
c("support", "maintain"),
c("support", "uphold"),
c("support", "sustain"),
c("sweet", "soft"),
c("sweet", "charming"),
c("sweet", "gentle"),
c("sword", "sabre"),
c("sword", "bayonet"),
c("sword", "rapier"),
c("sword", "dagger"),
c("sword", "spear"),
c("sword", "lance"),
c("sword", "truncheon"),
c("sword", "javelin"),
c("sword", "knife"),
c("sword", "weapon"),
c("sword", "hilt"),
c("sword", "scabbard"),
c("table", "desk"),
c("table", "sideboard"),
c("table", "chairs"),
c("taken", "given"),
c("taken", "brought"),
c("taken", "purloined"),
c("taken", "carried"),
c("taken", "removed"),
c("taken", "delivered"),
c("talk", "speak"),
c("talk", "listen"),
c("talk", "hear"),
c("taught", "instructed"),
c("taught", "tutored"),
c("taught", "trained"),
c("taught", "instructed"),
c("taught", "learned"),
c("taught", "learnt"),
c("tears", "sighs"),
c("tears", "lamentations"),
c("tears", "grief"),
c("tears", "sorrow"),
c("tears", "sobs"),
c("tears", "anguish"),
c("tears", "suffering"),
c("tears", "weeping"),
c("tears", "sorrows"),
c("tell", "know"),
c("tell", "hear"),
c("tell", "understand"),
c("tell", "say"),
c("tell", "inform"),
c("tell", "speak"),
c("tell", "state"),
c("tember", "disposition"),
c("tember", "behavior"),
c("tender", "soft"),
c("tender", "gentle"),
c("tender", "delicate"),
c("terms", "conditions"),
c("think", "presume"),
c("think", "know"),
c("think", "believe"),
c("think", "imagine"),
c("think", "suppose"),
c("think", "guess"),
c("think", "say"),
c("thought", "remembered"),
c("thought", "believed"),
c("thought", "imagined"),
c("thought", "guessed"),
c("thought", "fancied"),
c("thousand", "hundred"),
c("thousand", "fifty"),
c("thousand", "ten"),
c("thousand", "twenty"),
c("thousand", "million"),
c("throne", "monarch"),
c("throne", "king"),
c("throne", "queen"),
c("throne", "emperor"),
c("throne", "empress"),
c("throne", "crown"),
c("throne", "sceptre"),
c("throne", "diadem"),
c("throne", "scepter"),
c("time", "day"),
c("time", "night"),
c("time", "morning"),
c("time", "afternoon"),
c("time", "evening"),
c("time", "midnight"),
c("time", "sundown"),
c("time", "moment"),
c("time", "interval"),
c("time", "hour"),
c("time", "minute"),
c("times", "periods"),
c("times", "years"),
c("times", "weeks"),
c("times", "seasons"),
c("times", "ages"),
c("times", "days"),
c("times", "hours"),
c("times", "minutes"),
c("times", "seconds"),
c("times", "months"),
c("told", "informed"),
c("told", "said"),
c("told", "assured"),
c("told", "asked"),
c("tongue", "ear"),
c("tongue", "ears"),
c("tongue", "eyes"),
c("tongue", "eye"),
c("tongue", "nose"),
c("tongue", "throat"),
c("tongue", "mouth"),
c("tongue", "lips"),
c("town", "city"),
c("town", "village"),
c("town", "metropolis"),
c("town", "seaport"),
c("town", "precinct"),
c("town", "parish"),
c("town", "suburbs"),
c("town", "neighborhood"),
c("town", "boulevard"),
c("town", "outskirts"),
c("town", "highroad"),
c("town", "road"),
c("town", "house"),
c("town", "home"),
c("town", "country"),
c("town", "village"),
c("town", "city"),
c("town", "neighborhood"),
c("town", "seaport"),
c("town", "metropolis"),
c("town", "suburbs"),
c("town", "suburb"),
c("town", "country"),
c("town", "neighbourhood"),
c("town", "house"),
c("town", "townhouse"),
c("trade", "commerce"),
c("trade", "manufacturing"),
c("trade", "manufacture"),
c("trade", "export"),
c("trade", "merchant"),
c("trade", "merchants"),
c("trade", "commodity"),
c("trade", "commodities"),
c("trade", "factories"),
c("trade", "factory"),
c("tree", "cedar"),
c("tree", "oak"),
c("tree", "mulberry"),
c("tree", "poplar"),
c("tree", "elm"),
c("tree", "beech"),
c("tree", "willow"),
c("tree", "shrub"),
c("tree", "hedge"),
c("tree", "bush"),
c("tree", "grass"),
c("tree", "leaf"),
c("tree", "bough"),
c("tree", "boughs"),
c("tree", "fruit"),
c("tree", "twigs"),
c("trees", "shrubs"),
c("trees", "bushes"),
c("trees", "oaks"),
c("trees", "elms"),
c("trees", "beeches"),
c("trees", "cedars"),
c("trees", "pines"),
c("trees", "firs"),
c("trees", "boughs"),
c("trees", "foliage"),
c("trees", "vines"),
c("troops", "army"),
c("troops", "armies"),
c("troops", "soldiers"),
c("troops", "detachments"),
c("troops", "legions"),
c("troops", "regiments"),
c("troops", "fleets"),
c("troops", "auxiliaries"),
c("troops", "squadrons"),
c("troops", "battalions"),
c("troops", "cavalry"),
c("troops", "infantry"),
c("true", "false"),
c("true", "real"),
c("trust", "believe"),
c("trust", "confidence"),
c("trust", "belief"),
c("trust", "confide"),
c("trust", "expectation"),
c("trust", "expectance"),
c("trust", "betray"),
c("trust", "mislead"),
c("trust", "forswear"),
c("trust", "distrust"),
c("trust", "mistrust"),
c("truth", "lie"),
c("truth", "falsehood"),
c("truth", "sincerity"),
c("truth", "veracity"),
c("truth", "rectitude"),
c("truth", "honesty"),
c("truth", "verity"),
c("understand", "comprehend"),
c("understand", "know"),
c("understand", "perceive"),
c("understand", "imagine"),
c("understand", "believe"),
c("unhappy", "happy"),
c("unhappy", "glad"),
c("unhappy", "joyful"),
c("unhappy", "unfortunate"),
c("unhappy", "wretched"),
c("unhappy", "pitiable"),
c("unhappy", "miserable"),
c("unhappy", "heartbroken"),
c("unhappy", "sad"),
c("useful", "serviceable"),
c("useful", "helpful"),
c("useful", "beneficial"),
c("useful", "valuable"),
c("usual", "customary"),
c("usual", "ordinary"),
c("usual", "unusual"),
c("utmost", "greatest"),
c("utmost", "highest"),
c("utmost", "fullest"),
c("vain", "fruitless"),
c("vain", "boastful"),
c("vain", "haughty"),
c("variety", "diversity"),
c("variety", "multiplicity"),
c("variety", "assemblage"),
c("vast", "prodigious"),
c("vast", "immense"),
c("vast", "stupendous"),
c("vast", "enormous"),
c("vast", "huge"),
c("vast", "boundless"),
c("vast", "large"),
c("vast", "mighty"),
c("vast", "great"),
c("verse", "prose"),
c("verse", "rhyme"),
c("verse", "stanza"),
c("verse", "couplet"),
c("verse", "meter"),
c("verse", "metre"),
c("verse", "lyric"),
c("verse", "song"),
c("virtue", "piety"),
c("virtue", "rectitude"),
c("virtue", "nobleness"),
c("voice", "accents"),
c("voice", "tones"),
c("voice", "tone"),
c("voice", "sound"),
c("voice", "accent"),
c("voice", "ear"),
c("wait", "attend"),
c("wait", "tarry"),
c("wait", "await"),
c("wait", "stay"),
c("walk", "stroll"),
c("walk", "jog"),
c("walk", "saunter"),
c("walk", "ride"),
c("wanted", "wished"),
c("wanted", "needed"),
c("wanted", "desired"),
c("war", "campaign"),
c("war", "battles"),
c("war", "battle"),
c("war", "skirmish"),
c("war", "army"),
c("war", "armies"),
c("war", "general"),
c("war", "generals"),
c("war", "soldier"),
c("war", "soldiers"),
c("war", "enemy"),
c("war", "enemies"),
c("war", "ally"),
c("war", "allies"),
c("war", "peace"),
c("war", "conflict"),
c("war", "rebellion"),
c("war", "mutiny"),
c("war", "fight"),
c("war", "hostilities"),
c("war", "feud"),
c("war", "bloodshed"),
c("war", "death"),
c("warm", "cool"),
c("warm", "cold"),
c("warm", "hot"),
c("warm", "lukewarm"),
c("water", "ice"),
c("water", "pump"),
c("water", "ship"),
c("water", "boat"),
c("water", "trough"),
c("water", "bucket"),
c("water", "pitcher"),
c("water", "boiler"),
c("water", "basin"),
c("water", "liquid"),
c("way", "track"),
c("way", "path"),
c("way", "road"),
c("way", "course"),
c("way", "trail"),
c("way", "route"),
c("way", "passage"),
c("way", "method"),
c("weak", "strong"),
c("weak", "feeble"),
c("weak", "frail"),
c("weak", "impotent"),
c("weak", "faint"),
c("weak", "infirm"),
c("wealth", "riches"),
c("wealth", "opulence"),
c("wealth", "affluence"),
c("wealth", "poverty"),
c("weight", "load"),
c("weight", "burden"),
c("weight", "bulk"),
c("west", "east"),
c("west", "north"),
c("west", "south"),
c("west", "southwest"),
c("west", "southeast"),
c("west", "northwest"),
c("west", "northeast"),
c("white", "black"),
c("white", "brown"),
c("white", "blue"),
c("white", "red"),
c("white", "orange"),
c("white", "green"),
c("white", "purple"),
c("white", "gray"),
c("white", "grey"),
c("white", "color"),
c("white", "colour"),
c("whole", "entire"),
c("whole", "complete"),
c("whole", "compleat"),
c("whole", "remainder"),
c("whole", "part"),
c("wife", "husband"),
c("wife", "widower"),
c("wife", "widow"),
c("wife", "father"),
c("wife", "mother"),
c("wife", "aunt"),
c("wife", "uncle"),
c("wife", "grandfather"),
c("wife", "grandmother"),
c("wife", "grandparent"),
c("wife", "grandson"),
c("wife", "granddaughter"),
c("wife", "grandchild"),
c("wife", "niece"),
c("wife", "nephew"),
c("wife", "helpmate"),
c("wife", "child"),
c("wife", "parent"),
c("wind", "gale"),
c("wind", "storm"),
c("wind", "squall"),
c("wind", "breeze"),
c("wind", "squalls"),
c("wind", "storms"),
c("wind", "gusts"),
c("winter", "spring"),
c("winter", "autumn"),
c("winter", "summer"),
c("winter", "season"),
c("winter", "frosts"),
c("winter", "snow"),
c("winter", "frost"),
c("winter", "rain"),
c("wise", "prudent"),
c("wise", "circumspect"),
c("wise", "discreet"),
c("wise", "discerning"),
c("wish", "desire"),
c("wish", "hope"),
c("wish", "dream"),
c("wish", "believe"),
c("wished", "desired"),
c("wished", "hoped"),
c("wished", "wanted"),
c("wit", "talent"),
c("wit", "genius"),
c("wit", "taste"),
c("wit", "discernment"),
c("wit", "repartee"),
c("wit", "liveliness"),
c("wit", "vivacity"),
c("woman", "man"),
c("woman", "gentleman"),
c("woman", "gentlewoman"),
c("woman", "boy"),
c("woman", "girl"),
c("woman", "child"),
c("woman", "person"),
c("woman", "widow"),
c("woman", "wife"),
c("woman", "mother"),
c("woman", "daughter"),
c("woman", "aunt"),
c("woman", "grandmother"),
c("woman", "niece"),
c("woman", "maid"),
c("woman", "maiden"),
c("women", "people"),
c("women", "men"),
c("women", "persons"),
c("women", "fellows"),
c("women", "citizens"),
c("women", "folks"),
c("women", "men"),
c("women", "gentlewomen"),
c("women", "wives"),
c("women", "girls"),
c("women", "mothers"),
c("women", "ladies"),
c("women", "maids"),
c("women", "midwives"),
c("women", "mistresses"),
c("women", "maidservants"),
c("wonder", "astonishment"),
c("wonder", "amazement"),
c("wonder", "surprise"),
c("wonder", "surprize"),
c("wood", "shrubbery"),
c("wood", "thicket"),
c("wood", "forest"),
c("words", "expressions"),
c("words", "phrases"),
c("words", "sentences"),
c("words", "speeches"),
c("words", "ejaculations"),
c("words", "text"),
c("words", "texts"),
c("words", "utterances"),
c("words", "syllables"),
c("words", "language"),
c("words", "speech"),
c("words", "meaning"),
c("words", "sense"),
c("words", "meanings"),
c("words", "terms"),
c("words", "sounds"),
c("words", "accents"),
c("work", "labor"),
c("work", "task"),
c("work", "employment"),
c("work", "business"),
c("work", "housework"),
c("work", "service"),
c("work", "labour"),
c("work", "labors"),
c("work", "labours"),
c("work", "chores"),
c("world", "earth"),
c("world", "universe"),
c("world", "heaven"),
c("world", "kingdom"),
c("world", "nation"),
c("worse", "better"),
c("worth", "merit"),
c("worth", "value"),
c("worthy", "deserving"),
c("writing", "transcribing"),
c("writing", "penning"),
c("writing", "copying"),
c("writing", "reading"),
c("writing", "translating"),
c("writing", "spelling"),
c("writing", "publishing"),
c("written", "published"),
c("written", "compiled"),
c("written", "transcribed"),
c("written", "spoken"),
c("wrong", "right"),
c("year", "month"),
c("year", "day"),
c("year", "week"),
c("year", "hour"),
c("year", "minute"),
c("year", "second"),
c("year", "century"),
c("years", "months"),
c("years", "days"),
c("years", "weeks"),
c("years", "hours"),
c("years", "minutes"),
c("years", "seconds"),
c("years", "centuries"),
c("young", "old"),
c("young", "elderly"),
c("young", "aged"),
c("young", "inexperienced"),
c("young", "unexperienced"),
c("young", "fresh"),
c("young", "gawky"),
c("youth", "childhood"),
c("youth", "age"),
c("sight", "vision"),
c("sight", "eyesight"),
c("sight", "spot"),
c("sight", "observe"),
c("sight", "see"),
c("married", "divorced"),
c("married", "widowed")
  
            )

data_list = list()

for(fn in files_list) {
  
  wwp_model = read.vectors(fn)
  sims <- c()
  for(pairs in data)
  {
    vector1 <- c()
    for(x in wwp_model[[pairs[1]]]) {
      vector1 <- c(vector1, x)
    }
    
    vector2 <- c()
    for(x in wwp_model[[pairs[2]]]) {
      vector2 <- c(vector2, x)
    }
    
    sims <- c(sims, cosine(vector1,vector2))
    #f_name <- strsplit(fn, "/")[[1]][[2]]
    data_list[[fn]] <- sims
  }
  
}

for(pairs in data){
  rownames <- c(rownames, paste(pairs[1], pairs[2], sep = "-"))
}

results <- structure(data_list,
                     class     = "data.frame",
                     row.names = rownames
)

#If you want to give your results document a more specific name; you can edit "model-test-results" below. 
write.csv(file="output/model-test-results.csv", x=results)

```

